3D Magnetic modelling of ellipsoidal bodies

### 2017-01-27 manuscript/manuscript.tex
function g1 for triaxial ellipsoids

For triaxial ellipsoids (e.g., $a > b > c$), the demagnetization
factors obtained by solving Eq. \ref{eq:n-tilde-dagger-ii} 
are given by:
\begin{equation}
\tilde{n}^{\dagger}_{11} = \frac{abc}
{\left( a^{2} - c^{2} \right)^{\frac{1}{2}} 
\left( a^{2} - b^{2} \right)} 
\left[ F(\kappa, \phi) - E(\kappa, \phi) \right] \: ,
\label{eq:n-tilde-dagger-11-triaxial}
\end{equation}
\begin{equation}
\tilde{n}^{\dagger}_{22} = 
-\frac{abc}
{\left( a^{2} - c^{2} \right)^{\frac{1}{2}} 
\left( a^{2} - b^{2} \right)} 
\left[ F(\kappa, \phi) - E(\kappa, \phi) \right] + 
\frac{abc}
{\left( a^{2} - c^{2} \right)^{\frac{1}{2}} 
\left( b^{2} - c^{2} \right)} E(\kappa, \phi)
- \frac{c^{2}}{b^{2} - c^{2}}
\label{eq:n-tilde-dagger-22-triaxial}
\end{equation}
and
\begin{equation}
\tilde{n}^{\dagger}_{33} = 
-\frac{abc}
{\left( a^{2} - c^{2} \right)^{\frac{1}{2}} 
\left( b^{2} - c^{2} \right)} E(\kappa, \phi) +
\frac{b^{2}}{b^{2} - c^{2}} \: ,
\label{eq:n-tilde-dagger-33-triaxial}
\end{equation}
where $\kappa = \left[ \left( a^{2} - b^{2} \right) / 
\left( a^{2} - c^{2} \right) \right]^{\frac{1}{2}}$,
$\cos \phi = c/a$,
\begin{equation}
F(\kappa, \phi) = 
\int^{\phi}_{0} 
\frac{1}{\left( 1 - \kappa^{2} \sin^{2} \psi \right)^{\frac{1}{2}}}
d\psi \: ,
\label{eq:F-kappa-phi}
\end{equation}
and
\begin{equation}
E(\kappa, \phi) = 
\int^{\phi}_{0} 
\left( 1 - \kappa^{2} \sin^{2} \psi \right)^{\frac{1}{2}}
d\psi \: .
\label{eq:E-kappa-phi}
\end{equation}
The functions $F(\kappa, \phi)$ (Eq. \ref{eq:F-kappa-phi}) and 
$E(\kappa, \phi)$ (Eq. \ref{eq:E-kappa-phi}) are
called Legendre's normal elliptic integrals of the first and 
second kind, respectivelly. \citet{stoner1945} presented a 
detailed deduction of the demagnetization factors $\tilde{n}^{\dagger}_{11}$
(Eq. \ref{eq:n-tilde-dagger-11-triaxial}), $\tilde{n}^{\dagger}_{22}$
(Eq. \ref{eq:n-tilde-dagger-22-triaxial}) and $\tilde{n}^{\dagger}_{33}$
(Eq. \ref{eq:n-tilde-dagger-33-triaxial}). \citet{clark1986} presented similar
formulas, but without any proof.

@@

The elements $\tilde{n}^{\ddagger}_{ij}(\tilde{\mathbf{r}})$,
$i = 1, 2, 3$, $j = 1, 2, 3$, of the transformed depolarization tensor 
$\tilde{\mathbf{N}}^{\ddagger}(\tilde{\mathbf{r}})$ used to compute
the magnetic field $\Delta \tilde{\mathbf{H}}(\tilde{\mathbf{r}})$ 
(Eq. \ref{eq:delta-H-tilde}) and
the total-field anomaly $\Delta \tilde{T}(\tilde{\mathbf{r}})$
(Eqs. \ref{eq:delta-T-tilde} and \ref{eq:delta-T-tilde-approx}) 
are calculated according to Eq. \ref{eq:nij-tilde}, with 
$\tilde{f}(\tilde{\mathbf{r}})$ given by $\tilde{f}^{\ddagger}(\tilde{\mathbf{r}})$
(Eq. \ref{eq:fe-tilde}).

\begin{equation}
\tilde{n}^{\ddagger}_{ii}(\tilde{\mathbf{r}}) =
\frac{abc}{2}
\left( \frac{\partial \lambda}{\partial \tilde{r}_{i}} \, h_{i} \, \tilde{r}_{i}
- g_{i} \right)
\label{eq:n-tilde-dagger-ii}
\end{equation}

\begin{equation}
\tilde{n}^{\ddagger}_{ij}(\tilde{\mathbf{r}}) =
\frac{abc}{2} \left(
\frac{\partial \lambda}{\partial \tilde{r}_{i}} \, h_{j} \, \tilde{r}_{j} 
\right)
\label{eq:n-tilde-dagger-ij}
\end{equation}

\begin{equation}
h_{i} = \frac{1}{\left( e_{i}^{2} + \lambda \right) R(\lambda)}
\label{eq:hi}
\end{equation}

\begin{equation}
g_{i} = \int_{\lambda}^{\infty} \frac{1}{\left( e_{i}^{2} + u \right) R(u)} du
\label{eq:gi}
\end{equation}

@@

@@

@@

@@

%%f
%\begin{figure}[t]
%\includegraphics[width=8.3cm]{FILE NAME}
%\caption{TEXT}
%\end{figure}
%
%%% TWO-COLUMN FIGURES
%
%%f
%\begin{figure*}[t]
%\includegraphics[width=12cm]{FILE NAME}
%\caption{TEXT}
%\end{figure*}
%
%
%%% TABLES
%%%
%%% The different columns must be seperated with a & command and should
%%% end with \\ to identify the column brake.
%
%%% ONE-COLUMN TABLE
%
%%t
%\begin{table}[t]
%\caption{TEXT}
%\begin{tabular}{column = lcr}
%\tophline
%
%\middlehline
%
%\bottomhline
%\end{tabular}
%\belowtable{} % Table Footnotes
%\end{table}
%
%%% TWO-COLUMN TABLE
%
%%t
%\begin{table*}[t]
%\caption{TEXT}
%\begin{tabular}{column = lcr}
%\tophline
%
%\middlehline
%
%\bottomhline
%\end{tabular}
%\belowtable{} % Table Footnotes
%\end{table*}
%
%
%%% NUMBERING OF FIGURES AND TABLES
%%%
%%% If figures and tables must be numbered 1a, 1b, etc. the following command
%%% should be inserted before the begin{} command.
%
%\addtocounter{figure}{-1}\renewcommand{\thefigure}{\arabic{figure}a}
%
%
%%% MATHEMATICAL EXPRESSIONS
%
%%% All papers typeset by Copernicus Publications follow the math typesetting regulations
%%% given by the IUPAC Green Book (IUPAC: Quantities, Units and Symbols in Physical Chemistry,
%%% 2nd Edn., Blackwell Science, available at: http://old.iupac.org/publications/books/gbook/green_book_2ed.pdf, 1993).
%%%
%%% Physical quantities/variables are typeset in italic font (t for time, T for Temperature)
%%% Indices which are not defined are typeset in italic font (x, y, z, a, b, c)
%%% Items/objects which are defined are typeset in roman font (Car A, Car B)
%%% Descriptions/specifications which are defined by itself are typeset in roman font (abs, rel, ref, tot, net, ice)
%%% Abbreviations from 2 letters are typeset in roman font (RH, LAI)
%%% Vectors are identified in bold italic font using \vec{x}
%%% Matrices are identified in bold roman font
%%% Multiplication signs are typeset using the LaTeX commands \times (for vector products, grids, and exponential notations) or \cdot
%%% The character * should not be applied as mutliplication sign
%
%
%%% EQUATIONS
%
%%% Single-row equation
%
%\begin{equation}
%
%\end{equation}
%
%%% Multiline equation
%
%\begin{align}
%& 3 + 5 = 8\\
%& 3 + 5 = 8\\
%& 3 + 5 = 8
%\end{align}
%
%
%%% MATRICES
%
%\begin{matrix}
%x & y & z\\
%x & y & z\\
%x & y & z\\
%\end{matrix}
%
%
%%% ALGORITHM
%
%\begin{algorithm}
%\caption{…}
%\label{a1}
%\begin{algorithmic}
%…
%\end{algorithmic}
%\end{algorithm}
%
%
%%% CHEMICAL FORMULAS AND REACTIONS
%
%%% For formulas embedded in the text, please use \chem{}
%
%%% The reaction environment creates labels including the letter R, i.e. (R1), (R2), etc.
%
%\begin{reaction}
%%% \rightarrow should be used for normal (one-way) chemical reactions
%%% \rightleftharpoons should be used for equilibria
%%% \leftrightarrow should be used for resonance structures
%\end{reaction}
%
%
%%% PHYSICAL UNITS
%%%
%%% Please use \unit{} and apply the exponential notation

>>>>

For triaxial ellipsoids (e.g., $a > b > c$), the demagnetization
factors obtained by solving Eq. \ref{eq:n-tilde-dagger-ii} 
are given by:
\begin{equation}
\tilde{n}^{\dagger}_{11} = \frac{abc}
{\left( a^{2} - c^{2} \right)^{\frac{1}{2}} 
\left( a^{2} - b^{2} \right)} 
\left[ F(\kappa, \phi) - E(\kappa, \phi) \right] \: ,
\label{eq:n-tilde-dagger-11-triaxial}
\end{equation}
\begin{equation}
\tilde{n}^{\dagger}_{22} = 
-\frac{abc}
{\left( a^{2} - c^{2} \right)^{\frac{1}{2}} 
\left( a^{2} - b^{2} \right)} 
\left[ F(\kappa, \phi) - E(\kappa, \phi) \right] + 
\frac{abc}
{\left( a^{2} - c^{2} \right)^{\frac{1}{2}} 
\left( b^{2} - c^{2} \right)} E(\kappa, \phi)
- \frac{c^{2}}{b^{2} - c^{2}}
\label{eq:n-tilde-dagger-22-triaxial}
\end{equation}
and
\begin{equation}
\tilde{n}^{\dagger}_{33} = 
-\frac{abc}
{\left( a^{2} - c^{2} \right)^{\frac{1}{2}} 
\left( b^{2} - c^{2} \right)} E(\kappa, \phi) +
\frac{b^{2}}{b^{2} - c^{2}} \: ,
\label{eq:n-tilde-dagger-33-triaxial}
\end{equation}
where
\begin{equation}
F(\kappa, \phi) = 
\int^{\phi}_{0} 
\frac{1}{\left( 1 - \kappa^{2} \sin^{2} \psi \right)^{\frac{1}{2}}}
d\psi \: ,
\label{eq:F-kappa-phi}
\end{equation}
and
\begin{equation}
E(\kappa, \phi) = 
\int^{\phi}_{0} 
\left( 1 - \kappa^{2} \sin^{2} \psi \right)^{\frac{1}{2}}
d\psi \: ,
\label{eq:E-kappa-phi}
\end{equation}
with $\kappa = \left[ \left( a^{2} - b^{2} \right) / 
\left( a^{2} - c^{2} \right) \right]^{\frac{1}{2}}$ and
$\cos \phi = c/a$.
The functions $F(\kappa, \phi)$ (Eq. \ref{eq:F-kappa-phi}) and 
$E(\kappa, \phi)$ (Eq. \ref{eq:E-kappa-phi}) are
called Legendre's normal elliptic integrals of the first and 
second kind, respectivelly. \citet{stoner1945} presented a 
detailed deduction of the demagnetization factors $\tilde{n}^{\dagger}_{11}$
(Eq. \ref{eq:n-tilde-dagger-11-triaxial}), $\tilde{n}^{\dagger}_{22}$
(Eq. \ref{eq:n-tilde-dagger-22-triaxial}) and $\tilde{n}^{\dagger}_{33}$
(Eq. \ref{eq:n-tilde-dagger-33-triaxial}). \citet{clark1986} presented similar
formulas, but without any proof.

@@

The elements $\tilde{n}^{\ddagger}_{ij}(\tilde{\mathbf{r}})$,
$i = 1, 2, 3$, $j = 1, 2, 3$, of the transformed depolarization tensor 
$\tilde{\mathbf{N}}^{\ddagger}(\tilde{\mathbf{r}})$ used to compute
the magnetic field $\Delta \tilde{\mathbf{H}}(\tilde{\mathbf{r}})$ 
(Eq. \ref{eq:delta-H-tilde}) and
the total-field anomaly $\Delta \tilde{T}(\tilde{\mathbf{r}})$
(Eqs. \ref{eq:delta-T-tilde} and \ref{eq:delta-T-tilde-approx}) 
are calculated according to Eq. \ref{eq:nij-tilde}, with 
$\tilde{f}(\tilde{\mathbf{r}})$ given by $\tilde{f}^{\ddagger}(\tilde{\mathbf{r}})$
(Eq. \ref{eq:fe-tilde}).
By following \citet{clark1986}, the diagonal elements $\tilde{n}^{\ddagger}_{ii}$
and the off-diagonal elements $\tilde{n}^{\ddagger}_{ij}$, $i = 1, 2, 3$,
$j = 1, 2, 3$, are given by
\begin{equation}
\tilde{n}^{\ddagger}_{ii}(\tilde{\mathbf{r}}) =
\frac{abc}{2}
\left( \frac{\partial \lambda}{\partial \tilde{r}_{i}} \, h_{i} \, \tilde{r}_{i}
- g_{i} \right)
\label{eq:n-tilde-dagger-ii}
\end{equation}
and
\begin{equation}
\tilde{n}^{\ddagger}_{ij}(\tilde{\mathbf{r}}) =
\frac{abc}{2} \left(
\frac{\partial \lambda}{\partial \tilde{r}_{i}} \, h_{j} \, \tilde{r}_{j} 
\right) \: ,
\label{eq:n-tilde-dagger-ij}
\end{equation}
where
\begin{equation}
h_{i} = \frac{1}{\left( e_{i}^{2} + \lambda \right) R(\lambda)} \: ,
\label{eq:hi}
\end{equation}
\begin{equation}
g_{i} = \int_{\lambda}^{\infty} \frac{1}{\left( e_{i}^{2} + u \right) R(u)} du \: ,
\label{eq:gi}
\end{equation}
$e_{1} = a$, $e_{2} = b$, $e_{3} = c$, and 
$\frac{\partial \lambda}{\partial \tilde{r}_{i}}$
is defined in Appendix B (Eq. \ref{eq:dlambda}).
The functions $g_{i}$ (Eq. \ref{eq:gi}) are defined according
to the ellipsoid type.

@@

For triaxial ellipsoids (e.g., $a > b > c$), the functions
$g_{i}$ (Eq. \ref{eq:gi}) are defined as follows
\citep{clark1986}:

\begin{equation}
g_{1} = \frac{2}{\left( a^{2} - b^{2} \right) \left( a^{2} - c^{2} \right)^{\frac{1}{2}}}
\left[ F(\kappa, \phi) - E(\kappa, \phi) \right] \: ,
\label{eq:g1-triaxial}
\end{equation}
\begin{equation}
g_{2} = 
\label{eq:g2-triaxial}
\end{equation}
and
\begin{equation}
g_{3} = \: ,
\label{eq:g3-triaxial}
\end{equation}
where $F(\kappa, \phi)$ and $E(\kappa, \phi)$ are defined by
Eqs. \ref{eq:E-kappa-phi} and \ref{eq:F-kappa-phi},
but with 
$\sin \phi = \sqrt{\left( a^{2} - c^{2} \right)/\left( a^{2} + \lambda \right)}$.

@@

\section{Numerical simulations}

\subsection{Demagnetization factors}

Figure \ref{fig:fig1} TEXT TEXT TEXT Fig. \ref{fig:fig1} TEXT TEXT TEXT (Fig. \ref{fig:fig1})

\subsection{Ellipsoidal models}

\subsection{Susceptibility}

@@

\section{Code availability}

@@

%%f
%\begin{figure}[t]
%\includegraphics[width=8.3cm]{FILE NAME}
%\caption{TEXT}
%\end{figure}
%

%f
\begin{figure}[t]
\includegraphics[width=8.3cm]{figures/n_triaxial.pdf}
\caption{TEXT}
\label{fig:fig1}
\end{figure}

%%% TWO-COLUMN FIGURES
%
%%f
%\begin{figure*}[t]
%\includegraphics[width=12cm]{FILE NAME}
%\caption{TEXT}
%\end{figure*}
%
%
%%% TABLES
%%%
%%% The different columns must be seperated with a & command and should
%%% end with \\ to identify the column brake.
%
%%% ONE-COLUMN TABLE
%
%%t
%\begin{table}[t]
%\caption{TEXT}
%\begin{tabular}{column = lcr}
%\tophline
%
%\middlehline
%
%\bottomhline
%\end{tabular}
%\belowtable{} % Table Footnotes
%\end{table}
%
%%% TWO-COLUMN TABLE
%
%%t
%\begin{table*}[t]
%\caption{TEXT}
%\begin{tabular}{column = lcr}
%\tophline
%
%\middlehline
%
%\bottomhline
%\end{tabular}
%\belowtable{} % Table Footnotes
%\end{table*}
%
%
%%% NUMBERING OF FIGURES AND TABLES
%%%
%%% If figures and tables must be numbered 1a, 1b, etc. the following command
%%% should be inserted before the begin{} command.
%
%\addtocounter{figure}{-1}\renewcommand{\thefigure}{\arabic{figure}a}
%
%
%%% MATHEMATICAL EXPRESSIONS
%
%%% All papers typeset by Copernicus Publications follow the math typesetting regulations
%%% given by the IUPAC Green Book (IUPAC: Quantities, Units and Symbols in Physical Chemistry,
%%% 2nd Edn., Blackwell Science, available at: http://old.iupac.org/publications/books/gbook/green_book_2ed.pdf, 1993).
%%%
%%% Physical quantities/variables are typeset in italic font (t for time, T for Temperature)
%%% Indices which are not defined are typeset in italic font (x, y, z, a, b, c)
%%% Items/objects which are defined are typeset in roman font (Car A, Car B)
%%% Descriptions/specifications which are defined by itself are typeset in roman font (abs, rel, ref, tot, net, ice)
%%% Abbreviations from 2 letters are typeset in roman font (RH, LAI)
%%% Vectors are identified in bold italic font using \vec{x}
%%% Matrices are identified in bold roman font
%%% Multiplication signs are typeset using the LaTeX commands \times (for vector products, grids, and exponential notations) or \cdot
%%% The character * should not be applied as mutliplication sign
%
%
%%% EQUATIONS
%
%%% Single-row equation
%
%\begin{equation}
%
%\end{equation}
%
%%% Multiline equation
%
%\begin{align}
%& 3 + 5 = 8\\
%& 3 + 5 = 8\\
%& 3 + 5 = 8
%\end{align}
%
%
%%% MATRICES
%
%\begin{matrix}
%x & y & z\\
%x & y & z\\
%x & y & z\\
%\end{matrix}
%
%
%%% ALGORITHM
%
%\begin{algorithm}
%\caption{…}
%\label{a1}
%\begin{algorithmic}
%…
%\end{algorithmic}
%\end{algorithm}
%
%
%%% CHEMICAL FORMULAS AND REACTIONS
%
%%% For formulas embedded in the text, please use \chem{}
%
%%% The reaction environment creates labels including the letter R, i.e. (R1), (R2), etc.
%
%\begin{reaction}
%%% \rightarrow should be used for normal (one-way) chemical reactions
%%% \rightleftharpoons should be used for equilibria
%%% \leftrightarrow should be used for resonance structures
%\end{reaction}
%
%
%%% PHYSICAL UNITS
%%%
%%% Please use \unit{} and apply the exponential notation
